Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-11-28 paper/snakemajoranas.tex
Add formulas for analytics to paper

\comment{Majoranas are mostly made in hybrid NS structures.}
\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
\comment{The gap is small because of long trajectories.}
\comment{We show that zigzag geometry solves this problem in a controllable manner.}

@@

\section{Analytical estimate}

Quasi classical short junction calculation explaination.
Include all, later move stuff to the appendix if necessary.

\section{Numerical bandstructures}

>>>>

@@

\section{Analytical estimate}
\begin{align}
    &S = 
    &\left(
    \begin{array}{cc}
    r & t\\
    t & e^{-2 i q W} r\\
    \end{array}
    \right) 
    \\
    &r = &\left(
    \begin{array}{rr}
    e^{i \nu_{\arg}}\left(\omega_+ - \omega_-\right) & (\omega _+ + \omega _-)\\
    -(\omega _+ + \omega _-) & - e^{-i \nu _{\arg }} \left(\omega _+ - \omega _-\right)\\
    \end{array}
    \right)
    \\
    &t = e^{-i q W} &\left(
    \begin{array}{rr}
    e^{i \nu_{\arg}}\left(\beta_+ - \beta_-\right) & (\beta_+ + \beta_-)\\
    -(\beta_+ + \beta_-) & - e^{-i \nu _{\arg }} \left(\beta_+ - \beta_-\right)\\
    \end{array}
    \right)
\end{align}

\begin{align}
    \omega_\pm = \frac{1}{4} \left(\gamma _{\pm}+\delta _{\pm}\right)
    \\
    \beta_\pm = \frac{1}{4} \left(\gamma _{\pm}-\delta _{\pm}\right)
\end{align}
\begin{align}
    \gamma_\pm = \frac{q+i k_{\pm} \tan \left(\frac{W k_{\pm}}{2}\right)}{q-i k_{\pm} \tan \left(\frac{W k_{\pm}}{2}\right)} \\
    \delta_\pm = \frac{q-i k_{\pm} \cot \left(\frac{W k_{\pm}}{2}\right)}{q+i k_{\pm} \cot \left(\frac{W k_{\pm}}{2}\right)}
\end{align}
\section{Numerical bandstructures}
